Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-23 NEUROC/sec4-experiments.tex
更新了4.4

>>>>

% added by wangyunpan, 2020-12-23, ----start----
\paragraph{Effects on Accuracy}
%
We were also concerned about whether the accuracy would be significantly dropped after the use of sampling techniques
and the effect of batch size of accuracy.
%
For all datasets and sampling techniques, we had done experiments where the accuracy of GNNs varied with the batch size
and compared them with the experimental results of full-batch training.
%
In order to make the results more reliable, we had selected the optimal network structure for each GNN experiment under each dataset.
%
The optimal network structure is taken from the result corresponding to the highest accuracy in the hyperparameter experiment.
%
The highest accuracy under different learning rates was selected as the final accuracy result.
%
\figurename~\ref{fig:fig:exp_sampling_relative_batch_size_accuracy} shows the results (we only shows two datasets, amc and fli).
%

%
With the change of batch size, the accuracy relationship between GNNs is roughly the same.
%
For example, for neigbor sampler, the relationship between GNNs on \texttt{amc} was GCN < GGNN < GAT < GaAN and the relationship on \texttt{amc} was GCN > GGNN > GAT> GaAN.
%
But there was also a little exceptions (cluster sampler on \textt{amc}, relative batch size was 50\%).
%
To a certain extent, the increase of batch size could bring benefits to all GNNs.
%
However, for different datasets, the accuracy relationship between GNNs was not constant.
%
And this relationship was not related to model complexity.
%
In other words, it was not that the higher the algorithm complexity, the higher the corresponding accuracy.
%
For a specific dataset, in order to obtain high accuracy, the best model could only be selected by constantly trying various models.
%

When the batch size was small, as the batch size increased, the accuracy and the batch size would be positively correlated. 
%
However, when the batch size increases to a certain extent, there was no direct relationship between accuracy and batch size.
%
In other words, for sampling techniques, the batch size corresponding to the best accuracy may not be the maximum value, but may be another value. 
%
This phenomenon is consistent with the results in \cite{zeng2020_graphsaint}.

%
After using the sampling techniques, the optimal accuracy of some GNNs on certain datasets exceeded the accuracy of the full-batch training (neigbbor sampler on \texttt{amc}).
%
This showed that the application of sampling technology was very meaningful, because it may brought certain benefits to accuracy.
%
Different sampling techniques bring different gains to GNNs.
%
\begin{figure}[H]
    \centering
    \subfloat[Neighbor sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
    \subfloat[Neighbor sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}} \\
    \subfloat[Cluster sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
    \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
    \caption{Test Accuracy under different batch sizes. FULL means that the full graph participates in the training.}
    \label{fig:exp_sampling_relative_batch_size_accuracy}
\end{figure}

% added by wangyunpan, 2020-12-23, ----end----
